Generating Simulated Data

### 2021-03-31 docs/SimData.Rmd
write grow par files by era

  maxera <- growthpars %>% 
    filter(!is.na(Linf)) %>% 
    group_by(era) %>% 
    tally() %>%
    filter(n==11) %>%
    select(era)

  growthspp <- growthpars %>%
    filter(era==maxera) %>%
    select(species, psi, kappa, Linf, K, growthType) %>%
    pivot_longer(psi:growthType, names_to = "par") %>%
    pivot_wider(names_from = species, 
                values_from = value) %>%
    ungroup() %>%
    select(-era) %>%
    remove_rownames %>% column_to_rownames(var="par") %>%
    write.csv(paste0(o.name,"growth_species_NOBA_era",maxera,"_",s,".csv"))
}

>>>>

  # sadly doesn't work so just make a csv for each era and use the one with most spp
  # maxera <- growthpars %>% 
  #   filter(!is.na(Linf)) %>% 
  #   group_by(era) %>% 
  #   tally() %>%
  #   filter(n==1) %>%
  #   select(era)

  growthspp <- growthpars %>%
    select(species, psi, kappa, Linf, K, growthType) %>%
    pivot_longer(psi:growthType, names_to = "par") %>%
    pivot_wider(names_from = species, 
                values_from = value)

  growthspp.era <- split(growthspp, list(growthspp$era))

  for(era in names(growthspp.era)) {
    gpar <- growthspp.era[[era]] %>%
      ungroup()%>%
      select(-era) %>%
      remove_rownames() %>% 
      column_to_rownames(var="par") %>%
      write.csv(paste0(o.name,"growth_species_NOBA_era",era,"_",s,".csv"))
